---
title: "Facebook"
author: "User"
date: "2023-10-27"
output: html_document
---

```{r setup, include=FALSE}
# loading the required libraries
library(MASS)
library(broom)
library(dplyr)
library(ggplot2)
library(stringr)
library(survey)
library(readr)
library(readxl)
library(arsenal)
library(AER)

```


Import the facebook data set first
```{r, include=FALSE}
library(readxl)
Facebook <- read_excel("C:/Users/User/Desktop/2149634_Facebook.csv")
View(Facebook)
```

Create Categorical Variables
```{r}
#Create Categorical Variables
Facebook$Product = rep(0, nrow(Facebook))
Facebook$Product[Facebook$Category=="product"] = 1
Facebook$Inspiration = rep(0, nrow(Facebook))
Facebook$Inspiration[Facebook$Category=="inspiration"] = 1
Facebook$Photo = rep(0, nrow(Facebook))
Facebook$Photo[Facebook$Type=="Photo"] = 1
Facebook$Status = rep(0, nrow(Facebook))
Facebook$Status[Facebook$Type =="Status"] = 1
Facebook$Video = rep(0, nrow(Facebook))
Facebook$Video[Facebook$Type=="Video"] = 1

```

Remove Infinities
```{r}
#Remove Infinities
Facebook$Share2 <- ifelse(Facebook$Share == 0, 0.00001, Facebook$Share)

```

Transform Variables
```{r}
#Transform Variables
Facebook$log_LifetimePostTotalReach = log(Facebook$LifetimePostTotalReach)
Facebook$SquareRoot_LifetimePostTotalReach = (Facebook$LifetimePostTotalReach)^(1/2)
Facebook$log_LifetimePostReachByLiked = log(Facebook$LifetimePostReachByLiked)
Facebook$log_Share2 = log(Facebook$Share2)


```

Model Before Transformations
```{r}
#Model Before Transformations
modelBeforeTransporation = lm(LifetimePostTotalReach ~ Paid + Product + Inspiration
 + LifetimePostReachByLiked + Share, data=Facebook)

```

Final Model
```{r}
#Final Model
modelFacebook = lm(log_LifetimePostTotalReach ~ Paid + Product + Inspiration
 + log_LifetimePostReachByLiked + log_Share2, data=Facebook)
plot(residuals(modelFacebook))
abline(h=0, col="red", lty=2)

```

Residual Plot
```{r}
#Residual Plot
plot(fitted(modelFacebook), residuals(modelFacebook),
 ylab="Residuals", xlab="Fitted Values", 
 main="Residual Plot: \n Residuals vs. Fitted")
abline(h=0, col="red", lty=2)

```

```{r}
#Does not have constant variation
#Normal Q-Q Plot
qqnorm(residuals(modelFacebook))
qqline(residuals(modelFacebook), col="red", lty=2)

```

Collinearity
```{r}
#Collinearity
library(car)
vif(modelFacebook)
summary(modelFacebook)

```

EDA
```{r}
#EDA
plot(Facebook$log_LifetimePostReachByLiked, Facebook$log_LifetimePostTotalReach, 
 xlab="LifetimePostReachByLiked",
 ylab="LifetimePostTotalReach", 
 main="LifetimePostReachByLiked vs. LifetimePostTotalReach",
 pch=9, col="violet")

```

```{r}
#EDA
plot(Facebook$log_Share2, Facebook$log_LifetimePostTotalReach, 
 xlab="log_Share2",
 ylab="log_LifetimePostTotalReach", 
 main="log_Share2 vs. log_LifetimePostTotalReach",
 pch=9, col="violet")
```

Categorical Plot (Paid vs. LifetimePostTotalReach)

```{r}
#EDA
# Categorical Plot
boxplot(Facebook$LifetimePostTotalReach ~ Facebook$Paid, 
        xlab = "Paid",
        ylab = "Total Interactions",
        main = "Paid vs. LifetimePostTotalReach",
        col = c("lightblue", "lightgreen"))


```


Histogram Plot (Share2)
```{r}
#EDA
# Histogram Plot
hist(Facebook$Share2,
     xlab = "Share2",
     main = "Distribution of Share2 (Without Log)",
     col = "lightblue",
     breaks = 20)


```


Numerical Summary (Without Log Transformations):
```{r}

# Summary Statistics
summary(Facebook$Share2[Facebook$Paid == 0])  # Unpaid Posts
summary(Facebook$Share2[Facebook$Paid == 1])  # Paid Posts


```

Graphing Independent Variables Individually with Numerical Summary:

LifetimePostTotalReach
```{r}
# Histogram Plot for LifetimePostTotalReach
hist(Facebook$LifetimePostTotalReach, 
     xlab = "LifetimePostTotalReach",
     main = "Distribution of LifetimePostTotalReach (Without Log)",
     col = "lightblue", 
     breaks = 20)


```


Numerical Summary for LifetimePostTotalReach:

```{r}
summary(Facebook$LifetimePostTotalReach)


```



Paid (Categorical Variable)
```{r}
# Barplot for Paid (Categorical Variable)
barplot(table(Facebook$Paid), 
        xlab = "Paid",
        ylab = "Frequency",
        main = "Distribution of Paid Posts",
        col = "lightgreen")


```


Numerical Summary for Paid (Categorical Variable):

```{r}
table(Facebook$Paid)


```



Graphing Independent Variables Against Dependent Variable:

LifetimePostTotalReach vs. LifetimePostReachByLiked
```{r}
# Scatterplot for LifetimePostTotalReach vs. LifetimePostReachByLiked (Without Log)
plot(Facebook$LifetimePostTotalReach, Facebook$LifetimePostReachByLiked, 
     xlab = "LifetimePostTotalReach",
     ylab = "LifetimePostReachByLiked",
     main = "LifetimePostTotalReach vs. LifetimePostReachByLiked",
     pch = 9, col = "violet")


```



Graphing Log-Transformed Independent Variables Against Log-Transformed Dependent Variable:

log(LifetimePostTotalReach) vs. log(LifetimePostReachByLiked)
```{r}
# Scatterplot for log(LifetimePostTotalReach) vs. log(LifetimePostReachByLiked)
plot(log(Facebook$LifetimePostTotalReach), log(Facebook$LifetimePostReachByLiked), 
     xlab = "log(LifetimePostTotalReach)",
     ylab = "log(LifetimePostReachByLiked)",
     main = "log(LifetimePostTotalReach) vs. log(LifetimePostReachByLiked)",
     pch = 9, col = "violet")


```


Exploratory Data Analysis
```{r}
# Scatterplot for LifetimePostTotalReach vs Paid
plot(Facebook$LifetimePostTotalReach, Facebook$Paid, 
     xlab = "LifetimePostTotalReach",
     ylab = "Paid",
     main = "LifetimePostTotalReach vs Paid",
     pch = 9, col = "violet")

# Scatterplot for LifetimePostTotalReach vs Product
plot(Facebook$LifetimePostTotalReach, Facebook$Category == 2, 
     xlab = "LifetimePostTotalReach",
     ylab = "Product",
     main = "LifetimePostTotalReach vs Product",
     pch = 9, col = "violet")

# Scatterplot for LifetimePostTotalReach vs Inspiration
plot(Facebook$LifetimePostTotalReach, Facebook$Category == 3, 
     xlab = "LifetimePostTotalReach",
     ylab = "Inspiration",
     main = "LifetimePostTotalReach vs Inspiration",
     pch = 9, col = "violet")

# Scatterplot for LifetimePostTotalReach vs LifetimePostReachByLiked
plot(Facebook$LifetimePostTotalReach, Facebook$LifetimePostReachByLiked, 
     xlab = "LifetimePostTotalReach",
     ylab = "LifetimePostReachByLiked",
     main = "LifetimePostTotalReach vs LifetimePostReachByLiked",
     pch = 9, col = "violet")

# Scatterplot for LifetimePostTotalReach vs Share
plot(Facebook$LifetimePostTotalReach, Facebook$Share, 
     xlab = "LifetimePostTotalReach",
     ylab = "Share",
     main = "LifetimePostTotalReach vs Share",
     pch = 9, col = "violet")

# Scatterplot for log(LifetimePostTotalReach) vs log(LifetimePostReachByLiked)
plot(log(Facebook$LifetimePostTotalReach), log(Facebook$LifetimePostReachByLiked), 
     xlab = "log(LifetimePostTotalReach)",
     ylab = "log(LifetimePostReachByLiked)",
     main = "log(LifetimePostTotalReach) vs log(LifetimePostReachByLiked)",
     pch = 9, col = "violet")

# Scatterplot for log(LifetimePostTotalReach) vs log(Share)
plot(log(Facebook$LifetimePostTotalReach), log(Facebook$Share), 
     xlab = "log(LifetimePostTotalReach)",
     ylab = "log(Share)",
     main = "log(LifetimePostTotalReach) vs log(Share)",
     pch = 9, col = "violet")


# Barplot for Paid (Categorical Variable)
barplot(table(Facebook$Paid), 
        xlab = "Paid",
        ylab = "Frequency",
        main = "Distribution of Paid Posts",
        col = "lightgreen")


# Barplot for Product (Categorical Variable)
barplot(table(Facebook$Category == 2), 
        xlab = "Product",
        ylab = "Frequency",
        main = "Distribution of Product Posts",
        col = "lightblue")


# Histogram Plot for LifetimePostReachByLiked
hist(Facebook$LifetimePostReachByLiked,
     xlab = "LifetimePostReachByLiked",
     main = "Distribution of LifetimePostReachByLiked (Without Log)",
     col = "lightgreen",
     breaks = 20)

# Histogram Plot for Share
hist(Facebook$Share,
     xlab = "Share",
     main = "Distribution of Share (Without Log)",
     col = "lightblue",
     breaks = 20)

# Histogram Plot for LifetimePostTotalReach
hist(Facebook$LifetimePostTotalReach, 
     xlab = "LifetimePostTotalReach",
     main = "Distribution of LifetimePostTotalReach (Without Log)",
     col = "lightblue", 
     breaks = 20)




# Numerical Summary for Paid
table(Facebook$Paid)

# Numerical Summary for Product
table(Facebook$Category == 2)

# Numerical Summary for Inspiration
table(Facebook$Category == 3)

# Numerical Summary for LifetimePostReachByLiked
summary(Facebook$LifetimePostReachByLiked)

# Numerical Summary for Share
summary(Facebook$Share)

# Numerical Summary for Log LifetimePostTotalReach
summary(log(Facebook$LifetimePostTotalReach))

# Numerical Summary for Log LifetimePostReachByLiked
summary(log(Facebook$LifetimePostReachByLiked))

# Numerical Summary for Log Share
summary(log(Facebook$Share))

# Numerical Summary for Paid
table(Facebook$Paid)

# Numerical Summary for Product
table(Facebook$Category == 2)

# Numerical Summary for LifetimePostReachByLiked
summary(Facebook$LifetimePostReachByLiked)

# Numerical Summary for Share
summary(Facebook$Share)

# Numerical Summary for LifetimePostTotalReach
summary(Facebook$LifetimePostTotalReach)

```



```{r}


```











